The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
words about vetting models

@@

For the \kepler\ light curves, this procedure yields at least one candidate
event in about 10~percent of targets and the three highest signal-to-noise
events are investigated in the following step.

@@

We consider the following mean models and this list provides a qualitative
justification for each model:
\begin{itemize}
{\item a limb-darkened, exposure time integrated transit light curve,}
{\item a pure Gaussian Process model to capture stellar variability,}
{\item a single outlier to account for a bad data point,}
{\item a step function to describe sudden pixel sensitivity dropouts (SPSDs;
\dfmtodo{CITE}), and}
{\item a box to catch signals that are well fit by the search scalar but
insufficiently transit-like to be convincing.}
\end{itemize}
The functional forms of these models are given in Appendix \dfmtodo{SOME APP}.

\dfmfig{model-comp} shows representative events that fall into different
classes and the corresponding maximum-likelihood model.

>>>>

\newcommand{\modelname}[1]{{\textsf{#1}}}

@@

For the \kepler\ light curves, this procedure yields at least one candidate
event in about 1~percent of targets and the three highest signal-to-noise
events are investigated in the following step.

@@

We consider the following mean models and this list provides a qualitative
justification for each model:
\begin{itemize}
{\item \modelname{transit} -- a limb-darkened, exposure time integrated
transit light curve,}
{\item \modelname{variability} -- a pure Gaussian Process model to capture
stellar variability,}
{\item \modelname{outlier} -- a single outlier to account for a bad data
point,}
{\item \modelname{step} -- a step function to describe sudden pixel
sensitivity dropouts (SPSDs; \dfmtodo{CITE}), and}
{\item \modelname{box} -- a box to catch signals that are well fit by the
search scalar but insufficiently transit-like to be convincing.}
\end{itemize}
The functional forms of these models are given in Appendix \dfmtodo{SOME APP}.

\dfmfig{model-comp} shows representative events that fall into different
classes and the corresponding maximum-likelihood model.
For each candidate event, the BIC of each of these models is computed and the
event is only passed as a candidate if the \modelname{transit} model is
preferred to all the other models.
The \modelname{box} model is the most restrictive comparison, vetoing about
half of the candidate events in the \kepler\ light curves, followed by the
\modelname{variability} model.
To further restrict to non-grazing transits, we also reject events where the
best fit impact parameter is less than $1 - R_\mathrm{P} / R_\star$.
